Verifying Demonstrations

### 2017-10-05 protocol.tex
Adds details to protocol overview fig, prepares for distance bounding

\begin{frame}
\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & pid\gets PRF_{k_P}(cid) \\
      P\to W\colon & pid \\
      W\colon & wid\gets PRF_{k_W}(pid), \\
        & wsig\gets PRF_{k_W}(wid, t_s, l) \\
      W\to P\colon & (wid, t_s, l, wsig) \\
      W\to S\colon & (pid, wid, t_s, l, wsig) \\
      P\to S\colon & (pid, wid, t_s, l, wsig)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of message exchanges.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}
\end{frame}

@@

\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
us to \emph{verify the data spatially}.

If we include \iac{LP}, this will tie the proof to the physical location and, 
thus, solve \cref{SpatiallyRelated}.
The \ac{LP} is \enquote{witnessed} (signed) by other participants.
The \ac{LP} contains coarse coordinates of the location, which must be within 
the protest area to be valid.
This allows Bob the protester to move within the protest area to collect 
witnesses (signatures).
It also provides privacy since the location cannot be used to deanonymize Bob's 
proof --- e.g.\ to correlate the location in his proof with captured 
surveillance footage.

\mode<presentation>{%
\begin{frame}
  \begin{figure}
    \centering
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.Proof
      [.{wsig} {\(x,y\)} {$t_s$} ]
      {\dots}
      [.{wsig} {\dots} ]
      ]
    \end{tikzpicture}
  \end{figure}

  \begin{idea}[Spatial eligibility]
    \begin{itemize}
      \item Include \iac{LP} which is \enquote{witnessed} (signed) by other 
        participants.
      \item We have a coarse location, just within the protest area.
      \item This allows protesters to move around to collect signatures.
      \item This provides privacy for the location, e.g.\ cannot map to 
        surveillance cameras.
    \end{itemize}
  \end{idea}
\end{frame}
}

\mode<none>{%
\begin{frame}
  \begin{idea}[Transitive trust]
    \begin{itemize}
      \item Trusted journalist Jane attends to report.
      \item She witnesses Alice's proof.

      \item Alice witnesses Bob's proof.
      \item Alice's (secret key's) transportation is physically limited.
      \item Trust on Bob's proof is proportional to time from when Jane 
        witnessed Alice's proof.
    \end{itemize}
  \end{idea}
\end{frame}

\begin{frame}
  \begin{figure}
    \centering
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.Proof
      [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}tsig} {$t_s'$} ] ]
      {\dots}
      [.{wsig} {\dots} ]
      ]
    \end{tikzpicture}
  \end{figure}

  \begin{remark}
    \begin{itemize}
      \item Secret key in hardware.
      \item Alice's witness signature must depend on Jane's.
      \item High-precision relation to time?
    \end{itemize}
  \end{remark}
\end{frame}
}

We will introduce a notion of transitivity for trust in these proofs.
The \emph{trusted} journalist Jane attends the protest to report on it.
She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.
Now Alice's \ac{LP} can be trusted as correct at that point in time.
Alice's ability to travel is physically limited.
Thus a verifier can trust any \ac{LP} that Alice witnesses proportionally to 
the time that has passed since Jane witnessed Alice's \ac{LP}.
We can apply this argument recursively for any other participant's \ac{LP} that 
Alice has witnessed.
However, this requires some assumptions:
\begin{itemize}
  \item It is actually Alice's signing key must have physically limited travel.
    This can be assumed for signing keys that are embedded into hardware by 
    some trusted person.
  \item Alice's witness signature must depend on Jane's witness signature, to 
    prove that Alice signed after Jane.
\end{itemize}
\begin{remark}
  This probably requires high-precision timestamps, i.e.\ a trusted 
  time-stamping server must be available during the protest.
  Or the proofs must be submitted to the \ac{tposet} during the protest.
\end{remark}

>>>>

\begin{frame}
\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & cid\gets H(\text{manifesto}), \\
        & pid\gets PRF_{k_P}(cid) \\
      P\to W\colon & pid \\
      W\leftrightarrow P\colon & \text{perform distance bounding} \\
      W\colon & wid\gets PRF_{k_W}(pid), \\
        & wsig\gets PRF_{k_W}(wid, t_s, l) \\
      W\to P\colon & (wid, t_s, l, wsig) \\
      W\to S\colon & (pid, wid, t_s, l, wsig) \\
      P\to S\colon & (pid, wid, t_s, l, wsig)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of message exchanges.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}
\end{frame}

@@

According to \cref{SpatiallyRelated} Alice and Bob must bind their proofs 
(shares) spatially to the location, which would allow us to verify that they 
were actually in that location.
The role of the witnesses, e.g.\ Jane, is to provide this property.
Jane can do this by using a distance-bounding protocol to ensure that the secret 
associated with Alice or Bob must be within limited physical distance.

Alice will send her \(pid\) to Jane to start the witness protocol.
Then they do the distance bounding \dots
If Jane is convinced that Alice's secret is within the desired proximity, she 
will compute her witness identifier \(wid\) and witness signature \(wsig\) and 
send them to Alice.
